### 2017-09-30 TF-vldb2018/subsec-Qinc.tex

\sstab(1) When $\Delta P_1$ comes with a unit edge deletion $\delta_1$=$(\kw{SD},$ $\kw{ST})^-$,
\bfc is updated as shown in the second column of \bfc in Fig.~\ref{fig-auxiliary-structures}(b).
\identifyaffball identifies balls with type code $(1, 1)$ and $(1, 0)$ as \affballsx,
\ie $\ball{[\kw{PM_1},2]}$ and $\ball{[\kw{PM_2},2]}$.
Then \identifyaffball resets the two corresponding filtering codes in \bfc to $(1, 1)$.

@@

The proof is deferred to the full version~\cite{fullvldb18}.

@@

\begin{figure}[t!]
%\vspace{-2ex}
\begin{center}
{\small
\myhrule
\vspace{-2ex}
\mat{0ex}{
\sstab {\sl Input:\/} $M(P_{fi}, \ball{[v,r]})$, $\ball{[v,r]}$, pattern edge insertion $\delta$ = $(u,u')^+$.\\
{\sl Output:\/} $M(P_{fi}\oplus \delta, \ball{[v,r]})$.\\
\sstab \bcc \hspace{1ex} \= $\kw{RMv}:=\emptyset$;\\
\icc \> \For \Each $u \in V_{P}$ \Do $\matchs(u)$ := \{$w | (u,w) \in M(P_{fi}, \ball{[v,r]})$\};\\
\icc \> \For \Each node $w \in \matchs(u)$\eat{in $M(P_{fi},\ball{[v,r]})$} \Do\\
\icc \>\hspace{2ex}\= \If there exists no $(w, w')\in E_{\ball{[v,r]}}$ with $w' \in \matchs(u')$ \Then\\
\icc \>\>\hspace{2ex}\= $\kw{RMv}.\kw{push}([u,w])$;\\
\icc \> \For \Each node $w' \in \matchs(u')$\eat{$M(P_{fi},\ball{[v,r]})$} \Do\\
\icc \>\> \If there exists no $(w', w)\in E_{\ball{[v,r]}}$ with $w \in \matchs(u)$ \Then\\
\icc \>\>\> $\kw{RMv}.\kw{push}([u',w'])$;\\
\icc \> \While $\kw{RMv}\neq \emptyset$ \Do\\
\icc \>\hspace{2ex}\= $[u,w]:=\kw{RMv}.\kw{pop}$(); $\matchs(u):=\matchs(u)\setminus\{w\}$;\\
\icc \>\> \For \Each $(u,u')\in E_{P_{fi}}$ \Do\\
\icc \>\>\hspace{2ex}\= \For \Each $(w, w')\in E_{\ball{[v,r]}}$ with $w' \in \matchs(u')$ \Do\\
\icc \>\>\>\hspace{2ex}\= \If there is no $(w', w'')\in E_{\ball{[v,r]}}$ with $w'' \in \matchs(u)$ \Then\\
\icc \>\>\>\>\hspace{2ex}\= \kw{RMv}.\kw{push}([$u',w'$]);\\
\icc \> \If there is a node $u\in V_{P_{fi}}$ with $|\matchs(u)| = 0$ \Then $\matchs(\cdot):=\emptyset$;\\
\icc \> $M(P_{fi}\oplus \delta, \ball{[v,r]})$ := \{$(u,w) | u \in V_{P}, w \in \matchs(u)$\};\\
\icc \> \Return $M(P_{fi}\oplus \delta, \ball{[v,r]})$;
}
\vspace{-2.5ex} \myhrule
}
\end{center}
\vspace{-3ex}
\caption{Procedure \patedgeinsert} \label{alg-patedgeinsert}
\vspace{-5ex}
\end{figure}

>>>>

\sstab(1) $\Delta P_1$ comes with a unit edge deletion $\delta_1$=$(\kw{SD},$ $\kw{ST})^-$ on $P_{f_2}$, and
\bfc is updated accordingly as shown in the second column of \bfc in Fig.~\ref{fig-auxiliary-structures}(b).

\identifyaffball first identifies balls with type code $(1, 1)$ and $(1, 0)$ as \affballsx,
\ie $\ball{[\kw{PM_1},2]}$ and $\ball{[\kw{PM_2},2]}$, and then \identifyaffball resets the two corresponding filtering codes in \bfc to $(1, 1)$.

@@

%The proof is deferred to the full version~\cite{fullvldb18}.

@@

\begin{figure}[t!]
%\vspace{-2ex}
\begin{center}
{\small
\myhrule
\vspace{-2ex}
\mat{0ex}{
\sstab {\sl Input:\/} $M(P_{fi}, \ball{[v,r]})$, $\ball{[v,r]}$, pattern edge insertion $\delta$ = $(u,u')^+$.\\
{\sl Output:\/} $M(P_{fi}\oplus \delta, \ball{[v,r]})$.\\
\sstab \bcc \hspace{1ex} \= $\kw{RMv}:=\emptyset$;\\
\icc \> \For \Each $u \in V_{P}$ \Do $\matchs(u)$ := \{$w | (u,w) \in M(P_{fi}, \ball{[v,r]})$\};\\
\icc \> \For \Each node $w \in \matchs(u)$\eat{in $M(P_{fi},\ball{[v,r]})$} \Do\\
\icc \>\hspace{2ex}\= \If there exists no $(w, w')\in E_{\ball{[v,r]}}$ with $w' \in \matchs(u')$ \Then\\
\icc \>\>\hspace{2ex}\= $\kw{RMv}.\kw{push}([u,w])$;\\
\icc \> \For \Each node $w' \in \matchs(u')$\eat{$M(P_{fi},\ball{[v,r]})$} \Do\\
\icc \>\> \If there exists no $(w', w)\in E_{\ball{[v,r]}}$ with $w \in \matchs(u)$ \Then\\
\icc \>\>\> $\kw{RMv}.\kw{push}([u',w'])$;\\
\icc \> \While $\kw{RMv}\neq \emptyset$ \Do\\
\icc \>\hspace{2ex}\= $[u,w]:=\kw{RMv}.\kw{pop}$(); $\matchs(u):=\matchs(u)\setminus\{w\}$;\\
\icc \>\> \For \Each $(u,u')\in E_{P_{fi}}$ \Do\\
\icc \>\>\hspace{2ex}\= \For \Each $(w, w')\in E_{\ball{[v,r]}}$ with $w' \in \matchs(u')$ \Do\\
\icc \>\>\>\hspace{2ex}\= \If there is no $(w', w'')\in E_{\ball{[v,r]}}$ with $w'' \in \matchs(u)$ \Then\\
\icc \>\>\>\>\hspace{2ex}\= \kw{RMv}.\kw{push}([$u',w'$]);\\
\icc \> \If there is a node $u\in V_{P_{fi}}$ with $|\matchs(u)| = 0$ \Then $\matchs(\cdot):=\emptyset$;\\
\icc \> $M(P_{fi}\oplus \delta, \ball{[v,r]})$ := \{$(u,w) | u \in V_{P}, w \in \matchs(u)$\};\\
\icc \> \Return $M(P_{fi}\oplus \delta, \ball{[v,r]})$;
}
\vspace{-2.5ex} \myhrule
}
\end{center}
\vspace{-3ex}
\caption{Procedure \patedgeinsert} \label{alg-patedgeinsert}
\vspace{-4ex}
\end{figure}
